Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-11 paper/paper.tex
added `comment command'
Minor changes to sec 2 & 3

@@

Archival Chandra X-ray data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol. 
This lack of detection motivates our assumption that \lya emission is
powered by star formation only.

@@

\begin{equation}
\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
\label{eq:chi2}
\end{equation}
%
where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
model estimated flux.
As we do not have an analytic expression for $\hat{f}$; we use the
results of the Monte Carlo to build histograms that play the role of
$\hat{f}$.

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the difference between the lowest and highest $\chi^2$ values in
those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{min}=1200$.

Using the total number of degrees of freedom, $d.o.f.=104$ we divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$. 
We apply a random forest classification algorithm to find the
more relevant parameters in splitting the results into these two
classes. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

>>>>

\newcommand{\mg}[1]{\textcolor{blue}{\bf MG: \textit{#1}}}

@@

Archival Chandra X-ray data\footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol. 
This lack of detection motivates our assumption that \lya emission is
powered by star formation only.

@@

\begin{equation}
\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
\label{eq:chi2}
\end{equation}
%
where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
model estimated flux.
As we do not have an analytic expression for $\hat{f}$;
we obtain $\hat{f}$ from the binned results of the Monte Carlo radiative transfer simulations.

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the difference between the lowest and highest $\chi^2$ values in
those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{\mathrm{min}}=1200$.

Using the total number of degrees of freedom, $d.o.f.=104$ we divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}
We apply a random forest classification algorithm to find the
more relevant parameters in splitting the results into these two
classes. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.
